\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\setlist{nosep,leftmargin=1.6em}
\renewcommand{\arraystretch}{2.0}

\newcommand{\contactemail}{gengruixu@mail.ustc.edu.cn}

\begin{document}

\begin{center}
{\LARGE\bfseries mmAD Dataset Usage Agreement}\\[0.4em]
{\large mmGuard: A Countermeasure against Physical Adversarial Attacks on mmWave Radar Sensing}\\[0.3em]
{\normalsize IEEE Transactions on Information Forensics and Security (TIFS), 2026}
\end{center}

\vspace{0.5em}

This Agreement governs access to and use of the \textbf{mmAD} dataset (the
``Dataset'') and the accompanying \textbf{mmGuard} reference code (the
``Code''), released by the authors of the above publication (the
``Authors''). By signing this Agreement, the Recipient agrees to be bound by
the following terms.

\section{Permitted Use}
\begin{enumerate}[label=\arabic*.]
  \item The Dataset and Code are provided solely for \textbf{non-commercial
        academic research and educational purposes}.
  \item Any commercial use, including but not limited to use in a product,
        service, or for-profit activity, is strictly prohibited without prior
        written permission from the Authors.
\end{enumerate}

\section{Restrictions}
\begin{enumerate}[label=\arabic*.]
  \item The Recipient shall \textbf{not redistribute, publish, sell, lease,
        sublicense, or otherwise transfer} the Dataset or Code, in whole or in
        part, to any third party.
  \item The Recipient shall not share the download links or access credentials
        provided in the confirmation email with anyone outside the approved
        research group named below.
  \item The Recipient shall not attempt to re-identify any individual or
        infer private information from the Dataset.
  \item The Recipient shall not remove or alter any copyright, attribution, or
        proprietary notices contained in the Dataset or Code.
\end{enumerate}

\section{Attribution}
\begin{enumerate}[label=\arabic*.]
  \item Any publication, presentation, or work that makes use of the Dataset
        or Code must cite the mmGuard paper:\\[0.3em]
        \textit{R.\ Geng, D.\ Zhang, Y.\ Li, J.\ Wang, Q.\ Liang, R.\ Zhang,
        X.\ Xu, Z.\ Lu, Y.\ Hu, and Y.\ Chen, ``mmGuard: A Countermeasure
        against Physical Adversarial Attacks on mmWave Radar Sensing,'' IEEE
        Transactions on Information Forensics and Security, 2026.}
\end{enumerate}

\section{Disclaimer and Liability}
\begin{enumerate}[label=\arabic*.]
  \item The Dataset and Code are provided ``AS IS'', without warranty of any
        kind, express or implied. The Authors and their institutions make no
        warranties regarding accuracy, completeness, or fitness for a
        particular purpose.
  \item The Authors and their institutions shall not be held liable for any
        damages arising from the use of the Dataset or Code.
  \item The Authors reserve the right to terminate the Recipient's access at
        any time upon any breach of this Agreement.
\end{enumerate}

\section{How to Apply}
Please complete and sign the form below, scan it (or export it as a signed
PDF), and email it to \textbf{\contactemail}. Upon approval, you will receive
a confirmation email within two days containing a complete package with
\textbf{both} the Dataset download links and the mmGuard reference code.

\vspace{1em}
\hrule
\vspace{1em}

\section*{Recipient Information}

\begin{tabular}{@{}p{0.32\textwidth}p{0.62\textwidth}@{}}
Full Name: & \hrulefill \\
Position / Title: & \hrulefill \\
(e.g., Professor, PhD student) & \\
Institution / Organization: & \hrulefill \\
Department: & \hrulefill \\
Supervisor (if student): & \hrulefill \\
Institutional Email: & \hrulefill \\
Intended Research Use: & \hrulefill \\
 & \hrulefill \\
\end{tabular}

\vspace{1.5em}

I have read, understood, and agree to be bound by all terms of this Agreement.

\vspace{2em}

\begin{tabular}{@{}p{0.55\textwidth}p{0.40\textwidth}@{}}
Signature: \hrulefill & Date: \hrulefill \\
\end{tabular}

\vfill
\begin{center}
\small\textcolor{gray}{Project page: \href{https://ruixv.github.io/mmGuard/}{https://ruixv.github.io/mmGuard/} \quad|\quad Contact: \contactemail}
\end{center}

\end{document}
